Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-04-13 ltx/BrainIDE.tex
Updates and edits to paper

	\mathbf{x}_t &=& q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
	q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\

@@

Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations \cite{Sanner1992,Scerri2009}. Based on the higher dimension extensions of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.

Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited. Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions frequently used \cite{some eeg literature here}. Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually bandlimited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a bandlimited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.

@@

The approximation of the state density is made by propagating the so called sigma points through the state-space model. The sigma points describe the mean and covariance of the state estimate. The accuracy of the approximation is linked to the time step used in the temporal discretization of the system, where the state transition appears more linear with a finer resolution. To explain the operation of the UKF we begin by deriving the traditional Kalman filter with the state-space model
\begin{eqnarray}
	\mathbf{x}_t = q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{eqnarray}
where $\boldsymbol{\theta}$ and $\alpha$ are the systems parameters.

>>>>

	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
	q\left(\mathbf{x}_t\right) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\

@@

Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}. Based on the higher dimension extensions of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.

Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited. Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions frequently used \cite{some eeg literature here}. In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field. Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually bandlimited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a bandlimited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.

Sensors act as a low-pass filter

@@

The approximation of the state density is made by propagating the so called sigma points through the state-space model. The sigma points describe the mean and covariance of the state estimate. The accuracy of the approximation is linked to the time step used in the temporal discretization of the system, where the state transition appears more linear with a finer resolution. To explain the operation of the UKF we begin by deriving the traditional Kalman filter with the state-space model
\begin{eqnarray}
	\mathbf{x}_t = q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{eqnarray}
where $\boldsymbol{\theta}$ and $\lambda$ are the systems parameters.
